Reviving the Lost Art of \\Combinator Graph Reduction

### 2023-01-31 experiments/superg/doc/paper/paper.tex
Spelling.

The Lambda Calculus comes in many flavors.
The most basic version has only function abstraction and application, and is untyped.
Kiselyov's description of his new algorithms~\cite{kiselyov_lambda_2018} use a typed variant.
Our description of the translation is not defined as a type system, hence the untyped Lambda Calculus suffices for our treatment.
We do, however, enrich the Lambda Calculus with a few primitives that are convenient in a practical implementation. They are:
\begin{itemize}
    \item Machine integers (signed 32-bit). These can be emulated with e.g. Church Encoding, but arithmetic over a native integer type is faster.
    \item Arithmetic operations. To manipulate machine integers, we introduce the usual $+$, $-$, $*$ and $/$ operations.
    \item Comparison operations. To compare machine integers, we also add $==$, $<$ etc. These operations return $1$ if true, and $0$ if false (machine integers do double duty as a boolean type).
\end{itemize}

>>>>

The Lambda Calculus comes in many flavors.
The most basic version has only function abstraction and application and is untyped.
Kiselyov's description of his new algorithms~\cite{kiselyov_lambda_2018} uses a typed variant.
Our description of the translation is not defined as a type system, hence the untyped Lambda Calculus suffices for our treatment.
We do, however, enrich the Lambda Calculus with a few primitives that are convenient in a practical implementation. They are:
\begin{itemize}
    \item Machine integers (signed 32-bit). These can be emulated with e.g. Church Encoding, but arithmetic over a native integer type is faster.
    \item Arithmetic operations. To manipulate machine integers, we introduce the usual $+$, $-$, $*$ and $/$ operations.
    \item Comparison operations. To compare machine integers, we also add $==$, $<$ etc. These operations return $1$ if true, and $0$ if false (machine integers do double duty as a boolean type).
\end{itemize}
